---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gradeR

<!-- badges: start -->
<!-- badges: end -->

The goal of `gradeR` is to help grade bunches of `R` script assignment submissions. It is a one function package (`calcGrades()`), and most of the functionality is taken from the `testthat` package.

## Installation

<!-- You can install the released version of gradeR from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("gradeR") -->
<!-- ``` -->

<!-- And the development version from [GitHub](https://github.com/) with: -->

<!-- ``` r -->
<!-- # install.packages("devtools") -->
<!-- devtools::install_github("tbrown122387/gradeR") -->
<!-- ``` -->

You can install the development version of `gradeR` from with:

``` r
# install.packages("devtools")
devtools::install_github("tbrown122387/gradeR")
```

## Example

This is a basic example which shows you how to solve a common problem. Make sure to change the paths to ones that actually exist on your machine.

```{r example}
#library(gradeR)
#setwd("~/gradeR/example/")
#grades <- calcGrades("/path/to/assignment1_submissions/", "/path/to/grade_hw1.R")
```

The directory of the first argument will be walked recursively, and any function ending in a `.R` or `.r` will be ran and tested. The file with the tests is given by the second argument. For more information on how to write `testthat` tests, see [this.](https://cran.r-project.org/web/packages/testthat/testthat.pdf) 

